Fourmile Calibrations and Output

### 2025-05-02 fourmile_output_dec2024.Rmd
combined 2016 hydrograph with 2016 cumulative flows

flow_box <- ggplot(gw_maxcumsum, aes(x = source, y = flow_cms, fill = source)) +
  geom_boxplot(outliers=F,width=0.7) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
  geom_jitter(
    aes(shape = both),
    position = position_jitter(width = 0.25),
    size = 2.5,
    alpha = 0.7,
    stroke = 1,
    color = "black") +
  scale_shape_manual(values = c(
  "NSE + % bias unsatisfactory" = 4,
  "NSE + % bias satisfactory" = 16,
  "NSE satisfactory" = 1)) +
  geom_text(data = gw_maxcumsum_letters, 
            aes(label=letter,
                y=y_text),
            position = position_dodge(width = 0.97),
            size = 6, 
            vjust = 0) + 
  facet_wrap(~flow_type, 
             scales = 'free',
             labeller = labeller(flow_type = facet_labels)) +
  labs(y = 'mm of water') + 
  theme_bw(base_size=20) +
  scale_fill_manual(values = c("#0047AB", "orange"), guide = 'none') +
  theme(
    #legend.position = c(0.94, 0.36),
    legend.position = 'bottom',
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.x = element_blank(),
    legend.spacing = unit(0.1, "lines"),
    legend.margin = margin(t = -8, r = 0, b = -2, l = 0)) +
    #axis.text.x = element_blank(),
    #axis.ticks.x = element_blank()) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.15)))

@@

# ggsave('./figures/water_partition_boxplsource()# ggsave('./figures/water_partition_boxplots.png',
#        dpi=600)

@@

>>>>

flow_box <- ggplot(gw_maxcumsum, aes(x = source, y = flow_cms, fill = source)) +
  geom_boxplot(outliers=F,width=0.7) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
  geom_jitter(
    aes(shape = both),
    position = position_jitter(width = 0.25),
    size = 2.5,
    alpha = 0.7,
    stroke = 1,
    color = "black") +
  scale_shape_manual(values = c(
  "NSE + % bias unsatisfactory" = 4,
  "NSE + % bias satisfactory" = 16,
  "NSE satisfactory" = 1)) +
  geom_text(data = gw_maxcumsum_letters, 
            aes(label=letter,
                y=y_text),
            position = position_dodge(width = 0.97),
            size = 6, 
            vjust = 0) + 
  facet_wrap(~flow_type, 
             scales = 'free',
             labeller = labeller(flow_type = facet_labels)) +
  labs(y = 'mm of water') + 
  theme_bw(base_size=20) +
  scale_fill_manual(values = c("#0047AB", "orange"), guide = 'none') +
  theme(
    #legend.position = c(0.94, 0.36),
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.x = element_blank(),
    legend.spacing = unit(0.1, "lines"),
    legend.margin = margin(t = -8, r = 0, b = -2, l = 0)) +
    #axis.text.x = element_blank(),
    #axis.ticks.x = element_blank()) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.15)))

@@

ggsave('./figures/water_partition_boxplots.png',
       dpi=600,
       width = 12,
       height = 8)

@@

# Example year

# 2016 hydrograph
flowEg <- flow_pivot %>%
  filter(year %in% c(2016)) %>%
  ggplot(aes(x = date,
             y = q_m3s, 
             color = cal_run,
             linetype = cal_run)) + 
  geom_line(size = 1, alpha = 1) + 
  theme_bw(base_size = 20) +
  scale_color_manual(values = c("Gridded" = "#0047AB", 
                                "Observed" = "black", 
                                "Station" = "orange")) +
  scale_linetype_manual(values = c("Gridded" = "solid",
                                   "Observed" = "dashed", 
                                   "Station" = "solid")) +
  labs(x = element_blank(),
       y = "Streamflow (cms)") +
   scale_x_date(date_labels = "%b",
               date_breaks = "1 month") +
  theme(
    legend.position = c(0.9, 0.85),
    legend.text = element_text(size = 14),
    legend.key.width = unit(2, "lines"),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 2, r = 20, b = 2, l = 10)
  )

# 2016 flow partition
example <- gw %>%
  filter(year == 2016) %>%
  ungroup() %>% 
  dplyr::select(date, source,
         RD1cumsum,
         RD2cumsum,
         RG1cumsum,
         RG2cumsum) %>%
  pivot_longer(!c(date,source), names_to='flow_type',
               values_to='flow_cms') %>%
  mutate(source = if_else(source == 'grid_all',
                          'Gridded',
                          'Station'))

example_yr <- ggplot(example,
       aes(x=date, y = flow_cms, color=source)) +
  geom_line() +
  facet_wrap(~flow_type, 
             scales = 'free_y',
             labeller = labeller(flow_type = facet_labels)) +
   geom_line(size=1, alpha=0.7) +  
  scale_color_manual(values = c("#0047AB", "orange")) +
    scale_x_date(date_labels = "%b", 
               date_breaks = "2 month") +
  labs(x=element_blank(),
       y='mm of water') +
  theme_bw(base_size = 16) +
  theme(
    legend.position = 'none',
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 2, r = 20, b = 10, l = 10)
  )

plot_grid(flowEg,
          example_yr,
          ncol=1)

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/2016_all_flow.png',
       dpi=600,
       width=10,
       height=8)
